GSS Education Analysis (Working Title)

### 2023-03-15 outputs/paper/paper.qmd
remove figure 4 and update figure 6

```{r}
#| echo: false
#| warning: false
#| label: fig-4
#| fig-cap: "Respondent's Report of Job Satisfaction by Their Self-Ascribed Financial Ranking Against Other US Families"

#### Creating Graph to Compare Respondent's Report of Job Satisfaction by Their Self-Ascribed Financial Ranking Against Other US Families ####

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = finrela, fill = satjob)) +
  geom_bar() + 
  theme_classic() +
  labs(y = "Rating Against Other US Families",
       x = "Number of Respondents",
       fill = "Job Satisfaction")+
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```

```{r}
#| echo: false
#| warning: false
#| label: fig-5
#| fig-cap: "Respondent's Self-Asscribed Financial Ranking Against Other US Families by Their Reported Job Satisfaction"

#### Creating Graph to  ####

@@

```{r}
#| echo: false
#| warning: false
#| label: fig-6
#| fig-cap: "finrela vs class"

#### Creating Graph to ####

cleaned_gss_2021 |>
ggplot(mapping = aes(y = finrela, fill = class)) +
geom_bar() +
theme_classic() +
labs(y = "finrela",
x = "number",
fill = "class")+
scale_fill_brewer(palette = "Pastel1") +
theme(legend.title = element_text(size = 8),
legend.text= element_text(size=8))
```

# Discussion

## The American Dream

@@

## Social Class

@@

## Financial Satisfaction

@@

The second largest group of participants who had completed the survey had completed a bachelor's degree. In general, while a higher level of education improves access to better job opportunities, the process is not as linear as it may seem. According to @fig-2, while the number of individuals who have a graduate degree is not as high as the group that has completed a bachelor\'s degree, the reported financial ranking against other families was proportionately very similar for both groups. The majority for both groups claimed to be average or above average. There was still a significant number of individuals who had chosen below average, even for the group with the highest level of education.

A similar notion exists when comparing an individuals level of education with their job satisfaction. According to @fig-3, while most participants with an education level above high school, the majority group of individuals with a bachelor\'s or graduate degree still consists of those that chose \"Moderately Satisfied\", \"A Little Dissatisfied\", and \"Very Dissatisfied\". This points towards the unattainability of the American Dream, in that despite the greater level education and increased access that comes with it, it does not guarantee increased job satisfaction, or a higher financial satisfaction. According to @fig-4, the two highest levels of education still make up a significant portion of the \"More or Less Satisfied\" and the \"Not Satisfied at All'' groups.

## Limitations and weaknesses

@@

\

>>>>

```{r}
#| echo: false
#| warning: false
#| label: fig-5
#| fig-cap: "Respondent's Self-Ascribed Financial Ranking Against Other US Families by Their Reported Job Satisfaction"

#### Creating Graph to Compare Respondent's Self-Ascribed Financial Ranking Against Other US Families by Their Reported Job Satisfaction ####

@@

```{r}
#| echo: false
#| warning: false
#| label: fig-6
#| fig-cap: "Respondent's Self-Ascribed Financial Ranking Against Other US Families by Their Self-Ascribed Social Class"

#### Creating Graph to Compare Respondent's Self-Ascribed Financial Ranking Against Other US Families by Their Self-Ascribed Social Class ####

cleaned_gss_2021 |>
  ggplot(mapping = aes(y = finrela, fill = class)) +
  geom_bar() +
  theme_classic() +
  labs(
    y = "Rating Against Other US Families",
    x = "Number of Respondents",
    fill = "Social Class") +
  scale_fill_brewer(palette = "Pastel1") +
  theme(legend.title = element_text(size = 8),
        legend.text= element_text(size=8))
```

# Discussion {#sec-discussion}

## The American Dream {#sec-the-american-dream}

@@

## Social Class {#sec-social-class}

@@

## Financial Satisfaction {#sec-financial-satisfaction}

@@

The second largest group of participants who had completed the survey had completed a bachelor's degree. In general, while a higher level of education improves access to better job opportunities, the process is not as linear as it may seem. According to @fig-1, while the number of individuals who have a graduate degree is not as high as the group that has completed a bachelor\'s degree, the reported financial ranking against other families was proportionately very similar for both groups. The majority for both groups claimed to be average or above average. There was still a significant number of individuals who had chosen below average, even for the group with the highest level of education.

A similar notion exists when comparing an individuals level of education with their job satisfaction. According to @fig-2, while most participants with an education level above high school, the majority group of individuals with a bachelor\'s or graduate degree still consists of those that chose \"Moderately Satisfied\", \"A Little Dissatisfied\", and \"Very Dissatisfied\". This points towards the unattainability of the American Dream, in that despite the greater level education and increased access that comes with it, it does not guarantee increased job satisfaction, or a higher financial satisfaction. According to @fig-3, the two highest levels of education still make up a significant portion of the \"More or Less Satisfied\" and the \"Not Satisfied at All'' groups.

## Limitations and weaknesses {#sec-limitations-and-weaknesses}

@@

# Further reseach  {#sec-fur-reseach}
